---
title: "Weight of Fish"
author: "Onalee Garusinghe"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(car)
require(leaps)
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file = "Fish.csv")
```

```{r eval=TRUE}
 
fish <- fish %>%
mutate(across(where(is.character), as.factor))
levels(fish$Species)
Bream <- filter(fish, Species == "Bream")
Bream <- select(Bream, -Species) 
Parkki <- filter(fish, Species == "Parkki")
Parkki <- select(Parkki, -Species) 
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
Smelt <- filter(fish, Species == "Smelt")
Smelt <- select(Smelt, -Species) 
Whitefish <- filter(fish, Species == "Whitefish")
Whitefish <- select(Whitefish, -Species) 
```
Lepas 3 times for each fish.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
require(tidyverse)
if(!require("Bolstad")) {install.packages("Bolstad");require("Bolstad")}

data(bears)
Bears <- select(bears,contains("e"),-Name)
#Clean missing values out of dataset (needed to run Anova at end of demo)
Bears<- na.omit(Bears)
```

# For each of the three species of fish listed below, determine the best regression model and also the best 2 element regression model. Use the BestSubset Regression helper file.


## Perch

### Length 1
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottom",main="Adjusted R^2")
```

  This shows the Height and Width variables to be the best models. This also shows to be the best two variable model and can be proven using coding.

### Best Models
```{r}
which.max(summary.out$adjr2)
```
This shows that the model 2 is the best to express the data when looking at the adjusted R-squared value.

### Best Two regressor model
```{r}
summary.out$which[3,]
```
The best model of the perch fish is model 2, this data summary the best model has the highest adjusted R-squared value and that model has two variables meaning model 2 is the best two regression model.


## Pike
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

The best model appears to be model 5 including all L1, L2, L3, H, and W. variables. The best 2 regressor model appears to be model L1 and L3.

### Best Models
```{r}
which.max(summary.out$adjr2)
```

The model using all 5 variables is the best model.

### Best Two regressor model

Using leaps, we were able o focus its power onto the adjusted r-squared value. Then it would give us only the highest adjusted r-squared value for 1, 2, 3, 4, and 5 variables for pike. Using this kind of leap, it shows that L1 and L3 are the best 2 regressors for the highest adjusted r-squared value making it the best 2 regressor model.

## Roach

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomleft",main="Adjusted R^2")
```
The best models appear to be the model with 2 variables including L3 and W which means it i also the best 2 regressor model.

### Best Models

### Best Two regressor model

## Final Summary Statements


